DRAFT: v2 \\ Vibration Characterisation of Strollers and\\ Cargo Bicycles for Transporting Infants\\ \vspace{2mm} \large{Prepared for VeiligheidNL}

### 2025-01-27 main.tex
Update tex and bib file to version 2 from overleaf.

\title{
  DRAFT: v1 \\
  Vibration Characterization of Babies\\
  Transported in Strollers and Cargo Bicycles\\
  \vspace{2mm}
  \large{Prepared for VeiligheidNL}
}
\author{Gabriele Dell'Orto \and Brecht Daams \and Riender Happee \and Jason K. Moore}

@@

\section*{\centering Acknowledgements}
%
Thomas Valk and Jesper Meijerink helped design and perform the experiments.
Georgios Papaioannou and Arjo Loeve gave advice on the experimental design and
analyses.

\section{Introduction}
%
This paper reports on the vibration experienced by infants of different ages
when transported in cargo bicycles and strollers. Vibration can be related to
discomfort and might lead to negative health consequences. However, the topic is
poorly addressed in scientific literature, and only a few studies focus on the
effect of vibration on babies. To measure the actual vibration transmitted to
the babies, we equipped three strollers and two cargo bicycles with inertial
measurement units (IMU) and conducted several experiments across different road
surfaces and travelling speeds, using dummies representing the size of 0, 3, and
9 months old babies. We present analysis in the time and frequency domains,
allowing us to compare vertical accelerations at the baby-seat interface, as
recommended by ISO-2631-1. We investigate the influence of different variables
on vibration, such as type of vehicle, baby seat, travelling speed, dummy size
and mass, and road surfaces.

\section{Methods}
%
\subsection{Experimental Methodology}
%
In this section, we describe the measurement equipment used and the protocol
followed during the experimental campaign.

\subsubsection{Description of Test Equipment}
%
We conducted the experimental campaign using three different strollers, two
cargo bicycles, and two baby seats, chosen for their popularity and/or
distinctive features. The test involved three baby dummies representative of
various ages (different sizes and masses).

\paragraph{Strollers}
%
\begin{description}
  \item[Maxi-Cosi Street Plus] Among the most popular brands, this stroller comes
  with a cot configuration (0-3 months) and a baby seat option. It has large
  wheels, with only a marginal suspension system.
  (\href{https://www.maxi-cosi.nl/kinderwagens/street-plus?color_swatch_id=5519}{Maxi-cosi website})
  \item[Stokke BABYZEN YOYO 0+] It is the smallest foldable stroller on the
  market, it has only a marginal suspension system and smaller wheels compared
  to the other strollers on the market. It can be considered the ideal choice
  for holidays, being one of the few buggies that can be taken as hand
  luggage on the plane.
  (\href{https://tinylibrary.nl/products/kinderwagen-babyzen-yoyo-0-plus}{Model
  rented for the experiment})
  \item[Bugaboo Fox 5] It is featured by large wheels, and a suspension system
  which makes it an all-terrain stroller (according to the manufacturer). It has
  a large puncture-proof tyres and an air-permeable mattress.
  (\href{https://www.bugaboo.com/nl-nl/speciale-aanbiedingen/bugaboo-fox-5-bassinet-and-seat-stroller-black-base-midnight-black-fabrics-midnight-black-sun-canopy-PV006272.html?gad_source=1&gclid=Cj0KCQiA1Km7BhC9ARIsAFZfEIuB-6fQPRl5KyIHVJtion5lyD_Z1Qn-IP3shWoB_HXFozM1ySTXNfgaAgzFEALw_wcB&gclsrc=aw.ds}{Bugaboo
  website})
\end{description}

\paragraph{Cargo Bicycles}
%
\begin{description}
  \item[Urban Arrow Bicycle] This is a popular electric cargo bicycle in The
  Netherlands. This vehicle has two inline wheels which makes it roll into the
  curve like a regular bicycle. It is featured by a long frame that can carry
  loads usually placed in between the rider and the front wheel. It can fit
  various accessories, including baby seats, rain covers, etc.
  (\href{https://urbanarrow.com/}{Urban Arrow website})
  \item[Keiler Tricycle] This is a tadpole (two wheels in the front, one in the
  rear) cargo tricycle without electric assist. This vehicle will not roll in
  curves. However, differing road surface unevenness at the left and right front
  wheel will induce lateral roll and lateral acceleration in infants. We
  added masses in specific locations to simulate the presence of an electric
  motor and battery package.
 (\href{https://kashop.nl/product/keiler-bakfiets/}{Product Webpage}) 
\end{description}

\paragraph{Baby Seats}

These baby seats were mounted in the cargo bay of the two cargo bicycles.
%
\begin{description}
  \item[Maxi-Cosi X Joolz Pebble Pro i-Size Car Seat] This seat can be adapted to
    cargo bicycles with a proper fixing system (e.g. ``Urban Arrow Baby Car Seat
    Adapter''). It comes with an integrated suspension system which is part of
    the adapter.
    (\href{https://www.maxi-cosi.nl/autostoelen/pebble-pro-i-size}{Maxi-Cosi Webpage})
  \item[Melia Baby Shell]. The baby seat is meant for babies from 2 to 9 months,
    specifically designed for cargo bikes.
    (\href{https://melia.nl/product/babyschaal-4-seizoenen-comfort/}{Melia Webpage})
\end{description}

We conducted tests using three different dummies, of various sizes and masses
according to the desired ages of 0, 3 and 9 months. We considered the use of
``crash test dummies'' which are designed and commonly used to test
child seats in cars in crash conditions. However, the nearest available body
sizes for crash test dummies were a 6-weeks Q-dummy, a 6-months Crabi dummy, and a
12-months Q-dummy. These 3 dummies are of a fundamentally different design,
hampering comparison, and do not match the desired body size. Moreover, these
child dummies have dynamic properties designed for crash conditions, and use
scaling of adult biomechanical data, rather than child data.
Testing with real children would be unethical for the most severe conditions
tested, and would create challenges in terms of reproducibility.
Hence we bought and adapted dummies available in a wide range of postures. We
bought ``reborn'' dummies from a webshop specialising in dolls and dummies
(\href{http://www.atelier-wiesje.nl}{Atelier Wiesje}). We filled the dummies
with cat litter sand to reproduce the exact weight needed for testing. Cat
litter sand indeed features smooth and round-shaped grains, which do not
damage the dummies' material (fabric and plastic). The weight and body height of
the dummies are average measures for children of exactly 0, 3 and 9 months old.
We wanted to use the measurements from Steenbekkers \cite{Steenbekkers1993}. But
the researchers provided the results only per three-month group, which did not fit our
age categories. Therefore, we decided to use the growth charts to determine the average weight
and body height at the right ages. Growth charts (`groeidiagrammen') are used by
doctors to assess the growth of babies. The average weight at 0 months and the
average body height at all three ages are derived from Dutch growth charts.
Measurements of Dutch children are used because the Dutchies are the target group of
VeiligheidNL. Dutch children are also the tallest in Europe. The average weight
of 3 and 9 months children is derived from French growth charts. French children
are the smallest in Europe. At 3 months, the weight difference is 4 ounces and
at 9 months, it is 3 ounces compared to Dutch children.  
%
\begin{description}
  \item[Dummy 0 months] weight 3.48~\si{\kg}, size 50~\si{\cm}. Dollkit 20'',
  ``Andi Asleep'' (product code AW380008).
  (\href{http://www.atelier-wiesje.nl/index.php?item=9912---dollkit-20-_-andi-asleep--_-armen-_-_-benen----available&action=article&group_id=10000164&aid=2163&lang=NL}{Webpage})
  \item[Dummy 3 months] weight 5.90~\si{\kg}, size 62.5~\si{\cm}. Dollkit 25'',
  ``Asia - Limited Edition'' (product code 300287).
  (\href{http://www.atelier-wiesje.nl/index.php?action=article&aid=2556&group_id=10000176&lang=NL}{Webpage})
  \item[Dummy 9 months] weight 8.90~\si{\kg}. Size 70~\si{\cm}. Dollkit 28'',
  ``Hailey'' (product code 304137).
  (\href{http://www.atelier-wiesje.nl/index.php?action=article&aid=1974&group_id=10000133&lang=NL}{Webpage})
\end{description}

To achieve a realistic mass distribution in the body of the dummies, it is
important to fill each limb with the proper amount of sand. To do this, we
simplified the geometry of each body segment according to defined basic
geometric shapes: we assumed a sphere for the head, and cylinders for the torso,
upper arms, upper legs and lower legs, according to what was stated in
\cite{Snyder1977}. We also assumed an equal density of each limb, and we
rescaled the measurements of the limb segments reported in \cite{Snyder1977} to
match the dimensions of our dummies. In doing so, we were able to calculate the
volume of each segment, thus the mass of each limb of the dummies (assuming a
density of 1000~\si{\kg\per\cubic\meter}).

\subsubsection{Description of Measurement Equipment}

@@

Linear acceleration and angular velocity was measured using five IMUs.
Specifically, we used a Consensys Shimmer3 IMU with a Consensys Base 6U.01 dock.
The Shimmer units were updated to the firmware version LogAndStream v0.11.0, and
managed via the software ConsensysBASIC v1.6.0-64bit on a Laptop Dell 7310, OS
Microsoft Windows 10. We 3D printed supports for the sensors to ensure a firm

@@

listed below. The pictures of sensors mounted on the cargo bicycle Urban Arrow

@@

sensors for Urban Arrow equipped with the Melia baby shell are reported in

@@

Similarly, the Bugaboo configured to carry 0 months babies in the baby cot is

@@

  \subcaptionbox{Lateral view}{\includegraphics[width=75mm]{fig/TechDraw_UA_Melia_lateral.PNG}}
  \subcaptionbox{Front view}{\includegraphics[width=75mm]{fig/TechDraw_UA_Melia_front.PNG}}

@@

  \subcaptionbox{Lateral view}{\includegraphics[width=75mm]{fig/TechDraw_Bugaboo0_lateral.PNG}}

@@

  \item \textbf{Rear Wheel} The sensor was placed on the wheel hub (cargo
  bicycles) or clamped to the wheel (strollers). The purpose of this sensor is
  for a travel speed measurement. We can derive the travelling (longitudinal)
  speed according to:

@@

    v = \si{\omega} \cdot r

@@

  where \si{\omega} is the angular speed of the vehicle (from IMU gyroscope aligned with the wheel's axis) and $r$ is the radius of the wheel.
  \item \textbf{Front Wheel} The sensor was mounted on the front wheel fork (the
  caster wheel for the stroller). This is the measurement point closest to the
  ground for a non-rotating sensor. The purpose of this sensor is to measure the
  road roughness filtered out by the tyres.  
  \item \textbf{Frame} As for the cargo bicycle, the third sensor was placed
  below the frontal cargo bay, clamped to the frame. It can give us an

@@

  with an estimation of the effect of the suspension system. Regarding the
  stroller, the sensor was placed under the baby seat.
  \item \textbf{Seat Head} Sensor mounted into the baby seat, directly in
  contact with the dummy's head. It measured the vibration transmitted to the

@@

  \item \textbf{Seat Buttock} This sensor was taped into the baby seat, at the

@@

The IMU sensors for the seat head and seat buttock were placed at the surface at
positions contacting the dummy. This matches the recommended practice in
vibration testing norms such as ISO-2631-1. This generates acceleration data
representative of the mechanical load transferred from the seat to the human
body taking into account the compliance of the seat foams. We set the sampling
frequency to 910.22~\si{\hertz} for all the sensors. The full-scale range was
16~g for the accelerometer ("WR" or "wide range" configuration on Consensys
Shimmer software), and 2000~\si{\degree\per\second} for the gyroscope. All the
tests were recorded with two GoPro cameras Hero7: one directly mounted on the
strollers/bicycles to record the relative motion dummy/seat, while the other one
was held by an experimenter walking or riding alongside the vehicle to have a
complete overview of the experiment.

>>>>

% NOTE : Use as \si{\kph} or \si{\mps}
\def\kph{\kilo\meter\per\hour}
\def\mps{\meter\per\second}

\title{
  DRAFT: v2 \\
  Vibration Characterisation of Strollers and\\
  Cargo Bicycles for Transporting Infants\\
  \vspace{2mm}
  \large{Prepared for VeiligheidNL}
}
% Gabriele as first, Jason as last, alphabetical for intermediate (discuss in meeting if other method desired
\author{
Gabriele Dell'Orto \and
Brecht Daams \and
Riender Happee \and
Arjo J. Loeve \and
Jesper Meijerink \and
Georgios Papaioannou \and
Thomas Valk \and
Jason K. Moore
}

@@

\begin{abstract}
    TODO
\end{abstract}

\section{Introduction}
%
% Paragraph about motivation 
Cycling, one of the active transportation modes is advantageous for health~\cite{Oja1998} and greatly contributes to reducing CO2 emissions, congestion, and air
pollution ~\cite{Neves2019}.
As a result, bikes have been widely used as a mean to deliver goods to consumers, and also for daily commuting to work and personal matters (shopping, commuting with children/infants, and others).
Among all journeys in EU, 20-40$\%$ are by bike or on foot, with bicycle trips being most frequent in the Netherlands, Denmark and Sweden and less frequent in Finland.
Various countries and employers provide incentives to increase the use of bikes.
Nevertheless, there are great challenges that need to be overcome to secure the wide acceptance and use of active transportation modes.
One of these challenges is the comfort levels experienced by riders and passengers (i.e., infants/children in cargo bikes), which is a multi-faceted aspect \cite{ayachi2015identifying} and critical for the wide acceptance and use of bikes as a daily mean of transport.

% Paragraph about comfort in bikes
Comfort on bicycles \cite{too1990biomechanics} is mostly affected by physical comfort and the impact of environmental factors (weather, route geometry and road roughness).  
Physical comfort is related with mechanical (bicycle and components design), biomechanical (whole-body vibrations, human body dynamics and kinematics) and physiological factors (individual characteristics, e.g. sex, body size, weight and others).
While there is extensive literature exploring the impact of environmental factors (i.e., irregular road surface quality, weather conditions) on cyclists' comfort \cite{Stinson2003,Hagemeister2003,ayachi2015identifying,Verhoeven2017,Teixeira2020}, there is limited work on understanding the biomechanical and physiological factors of comfort while riding a bike or being driven by a bike (infants/children on cargo bikes or trailers).
In this paper, we will explore biomechanical comfort, by assessing the whole-body vibrations that could be experienced by transported infants, and evaluating potential health risks and discomfort that might arise.

% Paragraph about transmission of vibrations
Biomechanical comfort is mostly related to the vibrations induced by road irregularities and transmitted via the vehicle to the human body and head while being driven. 
According to the literature, the road irregularities are a critical factor for the amplitude of the resulting vibrations experienced by the bicyclists and passengers, as the vibrations induced on the body and head are not efficiently isolated due to the lack of suspension systems in most of the bike models \cite{vasudevan2017comparison}.
The bike design and its specific configuration can affect the sitting posture, and eventually the transmissibility of the vibrations \cite{Brand2020,Verma2016}.
The sitting posture can also vary in case of children/infants who may be transported sitting or lying down in a different--than the bicyclist--location (e.g. above a wheel when in a bike seat) and in/on a different ‘seat’ (a car seat, bike seat, stroller seat or cot). 
These all influence the level of whole-body vibrations and the transmission of the vibrations from the seat to the body and head. 
Furthermore, the amplitude of the vibrations experienced by bicyclists/passengers while biking or being transported may increase because of increased travelling speed either due to running with a stroller or due to the increased power offered by electric bikes (with and without trailers), and cargo bikes.
The average speed of electric bikes and speed pedelecs is 19$\%$ higher (21,0 km/h) and up to 63$\%$ higher (28,1 km/h), respectively, than the average speed of conventional bicycling (SWOV, 2022, p. 8).
The intensity of these vibrations could become even more critical with the change of load, which could be related with age and size of the infant/children transported. 
However, there is limited literature exploring the whole-body vibrations of infants and children being transported by bikes with trailers, cargo bikes or even cots \cite{Schwanitz2020,MalteChildComfort2022}.

% Paragraph about children in bikes
% 
One of the research fields closely related to vibrations acting on infants during transportation is that of inflicted head injury by shaking trauma (IHI-ST) (Vester, 2019; Zandwijk, 2019; Hutchinson, 2024). 
However, there is a lack of reliable, applicable, validated injury thresholds for assessing IHI-ST risks and hardly any chance that these thresholds do apply to vibration studies.
Similarly, even if there are significant indications that the vibration amplitude affects comfort in bikes or strollers, there are no standard assessment methods or guidelines available with regards to their design. 
ISO 2631, the international standard for assessing whole-body vibrations, was derived using datasets on motion platforms, adults as human participants and sitting postures which are adopted in passenger vehicles rather than in bikes.
This inconsistency was captured by Gao et al. (2018), who derived different limits of comfort for adults compared to ISO-2631.
In addition, the exposure time to the vibrations is not considered as a factor of comfort by the ISO2631, despite having a clear impact on health risks according to the European Directive (2002/44/EC, 2002).

% Paragraph Potential effects of vibrations on adults
Despite the lack of clarity with regards to comfort assessment or inflicted head injury by shaking trauma for children/infants on bikes, there are clear indications in the literature that these should be explored. 
About 36$\%$ of males and 42$\%$ of females in the total sample of 900 people (Groenendijk et al., 1992) had various complaints about comfort.
Discomfort for both men and women occurred even during short bicycle trips (3—10 km). 
Duarte et al. (2018) considered four different exposure durations and concluded that their results rejected the hypothesis that the exposure duration or the vibration dose value (VDV) by itself are important parameters on the vibration influence.
Furthermore, cyclists can avoid or reduce shocks and uncomfortable vibrations for a short time by standing on the pedals, which can increase comfort in some situations. 
This is an option that children sitting or lying in transportation systems do not have.
Results from research into comfort of adult cyclists are assumed to be children sitting or lying in transportation systems, leading potentially to misinterpretations. 
Hence, there is a need to re-focus on the impact of vibrations on infants and children health and comfort \cite{rybarczyk2020physiological} to secure the safe, comfortable and wide use of bikes.

Schwanitz et al. (2020a and 2020b) measured seat pan accelerations of a child bicycle trailer with anthropomorphic children shaped sandbag dummies (baby and toddler sizes) present in the seats. 
They report ISO 2631-1 weighted RMS vertical accelerations riding over smooth asphalt, gravel, and cobblestones. 
Tire pressure and the number of passengers had no significant effect on vibration magnitude, but road surface and travel speed did. 
The baby sized dummy (5 kg) experienced 20$\%$ higher vibration than the toddler sized dummy (10 kg). 
They express that their measured values generally exceed the ISO 2631-1 occupational norms for 4-8 hour vibrational comfort of adults.

Kayna-Forster (2020) measured acceleration in bicycle child trailers with human subjects aged 12 months to 6 years over asphalt and gravel terrain. 
The bicyclists travelled at their chosen comfort speeds and averaged 12 km/h over the 20 minute ride duration. According to the assessment using ISO-2631 and the use of an unspecified correction, the vibrations are similar to the ones experienced in car seats in vehicles and illustrated moderate or low health risk for a 2 hour duration. 
On the other hand, the uncorrected values point to moderate and high risks, which align with subsequent studies detailed below.
As expected, she also pointed out that cargo trailers with suspension systems did exhibit lower seat accelerations. 
Her second study utilised a laboratory vibration excitation system, similar to Ota et al. (2012) to determine the impact of independent variables (terrain type, trailer type, and cushion type) to the dependent variable vibration magnitude at the interface between the trailer seat and dummy buttock of a child. 
Terrain type had the greatest influence on vibration exposure levels followed by trailer type (p<0,001). 
Adding gel cushions did not significantly influence vibration measured at the seat/buttock interface.

Whole-body vibration by means of vibration total values obtained at toddler and baby dummy in dependence on different road surfaces, load cases, tire pressures, and velocities. Vibration discomfort threshold value 2.0 m/s2 is indicated with a dashed line. (Schwanitz et al., 2020a)
Liu (2023) developed a benchtop vibration excitation system for a unsuspended bicycle trailer capable of applying controlled and simulated road vibrations to the trailer. They measured IS0 2631-1 weighted RMS vertical accelerations at the seat pan ranging from 2,8 to 3,6 m/s2 for seat masses of 0 kg to 23 kg. Vibration increased with load at a high tire pressure (150 kPa) and had less variation at a lower pressure (75 kPa). They point out that these values are rated as “extremely uncomfortable” as per the 4-8 hour ISO 2631-1 occupational norms.
Rothhämel (2023) found ISO 2631-1 weighted RMS child trailer seat pan acceleration between 1 and 5 m/s2 for speeds between 10 and 20 km/h on smooth asphalt with large tire pressure variations having small effects. On cobblestones this range increased to 2 to 9 m/s2 for the same speed range. The child trailer exhibited larger weighted RMS vibration than a tadpole configuration three-wheel cargo bicycle with the child seat between the front wheels. Both the trailer and cargo bicycle child seats had generally larger magnitude vibrations than experienced in an automobile seat travelling at 30 km/h on a rough road (~3 m/s2) (Gromadowski 2013).
Rothhämel and Liu (2023) made improvements to the work by Lui (2023). They used the benchtop excitation device and the bicycle trailer with a 6,5 kg mass representing an infant and measured seat pan vertical acceleration at 2047 Hz sampling rate with excitation bandwidth of 17 Hz. They report ISO 2631-1 weighted vertical RMS ranging from 3 to 5 m/s2 for tire pressures from 50 to 400 kPa, which are higher value accelerations than reported by Liu (2023), See Figure 16. These values also fall into the “extremely uncomfortable” zone for the ISO 2631-1 4-8 hour occupational norms.

This paper reports on the vibration induced on infants of different ages when transported in strollers and cargo bicycles. 
Vibration can be related to discomfort and might lead to negative health consequences.  
In fact, vibrations induced by such transportation means have brought up as alternative scenarios in court cases concerning suspicion of infant injuries inflicted by violent shaking, such as in a recent case about a twin in 2023 in the Netherlands.
However, the topic is poorly addressed in scientific literature, and only a few studies focus on the effect of vibration on babies. 
To measure the actual vibration transmitted to the babies, we equipped five strollers and two cargo bicycles with inertial measurement units (IMU) and conducted several experiments on different road surfaces and travel speeds,
using dummies representing the size and mass of 0, 3, and 9 months old infants.
We present results in the time and frequency domains,
which allows comparing vertical accelerations at the baby-seat interface, as
recommended by ISO-2631-1 norms for vibration discomfort. 
We investigated the influence of different variables on vibration, such as type of vehicle, baby seat, travelling speed, dummy size and mass, and road surfaces.

\section{Methods}
%
\subsection{Experimental Methodology}
%
\subsubsection{Test Equipment}
%
Vibration measurements were conducted at approximate constant speed using five
different strollers, two cargo bicycles, and two baby seats, chosen for their
popularity and/or distinctive features:

\paragraph{Strollers}
%
\begin{description}
  \item[Maxi-Cosi Street Plus] Among the most popular brands, this stroller comes
  with a cot configuration (0-3 months) and a baby seat option. It has large
  wheels, with only a marginal suspension system.
  (\href{https://www.maxi-cosi.nl/kinderwagens/street-plus?color_swatch_id=5519}{Maxi-cosi website})
  \item[Stokke BABYZEN YOYO 0+] The smallest foldable stroller on the
  market. It has only a marginal suspension system and smaller wheels compared
  to the other strollers on the market. 
  (\href{https://tinylibrary.nl/products/kinderwagen-babyzen-yoyo-0-plus}{Model
  rented for the experiment})
  \item[Bugaboo Fox 5] Featured by large wheels and a suspension system
  that makes it an all-terrain stroller according to the manufacturer. It has
  a large puncture-proof tyres and an air-permeable mattress.
  (\href{https://www.bugaboo.com/nl-nl/speciale-aanbiedingen/bugaboo-fox-5-bassinet-and-seat-stroller-black-base-midnight-black-fabrics-midnight-black-sun-canopy-PV006272.html?gad_source=1&gclid=Cj0KCQiA1Km7BhC9ARIsAFZfEIuB-6fQPRl5KyIHVJtion5lyD_Z1Qn-IP3shWoB_HXFozM1ySTXNfgaAgzFEALw_wcB&gclsrc=aw.ds}{Bugaboo
  website})
\end{description}

\paragraph{Cargo Bicycles}
%
\begin{description}
  \item[Urban Arrow Bicycle] A popular electric cargo bicycle in The
  Netherlands. This vehicle has two inline wheels which makes it roll into curves like a regular bicycle. It is featured by a long frame that can carry
  loads usually placed in between the rider and the front wheel. 
  (\href{https://urbanarrow.com/}{Urban Arrow website})
  \item[Keiler Tricycle] A tadpole cargo tricycle (two wheels in the front, one in the
  rear) without electric assist. This vehicle will not roll into
  curves. However, differing road surface unevenness at the left and right front
  wheel will induce lateral roll and lateral acceleration in infants. We
  added masses in specific locations to simulate the presence of an electric
  motor and battery package.
 (\href{https://kashop.nl/product/keiler-bakfiets/}{Product Webpage}) 
\end{description}

\paragraph{Baby Seats}
%
These baby seats were mounted in the cargo bays of the two cargo bicycles.
%
\begin{description}
  \item[Maxi-Cosi X Joolz Pebble Pro i-Size Car Seat] Can be adapted to
    cargo bicycles with a fitting fixing system (e.g. ``Urban Arrow Baby Car Seat
    Adapter''). Comes with an integrated suspension system.
    (\href{https://www.maxi-cosi.nl/autostoelen/pebble-pro-i-size}{Maxi-Cosi Webpage})
  \item[Melia Baby Shell] Meant for babies from 2 to 9 months old,
    specifically designed for cargo bikes.
    (\href{https://melia.nl/product/babyschaal-4-seizoenen-comfort/}{Melia Webpage})
\end{description}
%
Appendix~\ref{app:equipment} provides figures and technical descriptions of all the strollers and cargo bicycles.

The tests involved three baby dummies with sizes and weights representative of 0, 3 and 9 months old infants. We considered the use of
``crash test dummies'' (also known as anthropomorphic test devices or ATD's) which are designed and commonly used to test
child seats in cars crash tests. However, the nearest available body
sizes for crash test dummies were a 6-weeks Q0-dummy, a 6-months Crabi dummy, and a
12-months Q-dummy. These 3 dummies are of a fundamentally different design,
hampering comparison, and do not match the desired body sizes. Moreover, these
child dummies have dynamic properties designed for crash conditions, and were designed based on
scaling of adult biomechanical data rather than child data.
Testing with real children would be unethical for the most severe conditions
tested, and would create challenges in terms of reproducibility.
Hence we bought and adapted ``reborn'' dummies available in a wide range of postures from a webshop specialising in dolls and dummies
(\href{http://www.atelier-wiesje.nl}{Atelier Wiesje}). The dummies
were filled with a mixture of cat litter sand and water to reproduce the exact weights needed for testing. Cat
litter sand features smooth and round-shaped grains, which do not
damage the dummies' materials (fabric and plastic). The weight and body height of
the dummies were made to match the are average measures for children of 0, 3 and 9 months old.
We wanted to use the measurements from Steenbekkers \cite{Steenbekkers1993}. But
the researchers provided the results only per three-month group, which did not fit our
age categories. Therefore, we decided to use the growth charts (used by clinicians to assess infant growth) to determine the average weight
and body height at the right ages. The average weight at 0 months and the
average body height at all three ages are derived from Dutch growth charts.
Measurements of Dutch children are used because these are the target group of
VeiligheidNL. Dutch children are also the tallest in Europe. The average weight
of 3 and 9 months children is derived from French growth charts. French children
are the smallest in Europe. At 3 months, the weight difference is 4 ounces and
at 9 months, it is 3 ounces compared to Dutch children.  
%
\begin{description}
  \item[Dummy 0 months] weight 3.48~\si{\kg}, size 50~\si{\cm}. Dollkit 20'',
  ``Andi Asleep'' (product code AW380008).
  (\href{http://www.atelier-wiesje.nl/index.php?item=9912---dollkit-20-_-andi-asleep--_-armen-_-_-benen----available&action=article&group_id=10000164&aid=2163&lang=NL}{Webpage})
  \item[Dummy 3 months] weight 5.90~\si{\kg}, size 62.5~\si{\cm}. Dollkit 25'',
  ``Asia - Limited Edition'' (product code 300287).
  (\href{http://www.atelier-wiesje.nl/index.php?action=article&aid=2556&group_id=10000176&lang=NL}{Webpage})
  \item[Dummy 9 months] weight 8.90~\si{\kg}. Size 70~\si{\cm}. Dollkit 28'',
  ``Hailey'' (product code 304137).
  (\href{http://www.atelier-wiesje.nl/index.php?action=article&aid=1974&group_id=10000133&lang=NL}{Webpage})
\end{description}

To achieve a realistic mass distribution in the body of the dummies, each limb was filled with a proper amount of sand. To do this, the geometry of each body segment was simplified according to pre-defined basic geometric shapes: a sphere for the head, and cylinders for the torso,
upper arms, upper legs and lower legs, according to \cite{Snyder1977}. We also assumed an equal density of each limb, and rescaled the measurements of the limb segments reported in \cite{Snyder1977} to match the dimensions of our dummies. In doing so, we were able to calculate the volume of each segment, and thus the mass of each limb of the dummies (assuming a
density of 1000~\si{\kg\per\cubic\meter}).

\subsubsection{Measurement Equipment}

@@

Linear accelerations and angular velocities were measured tri-axially using Consensys Shimmer3 IMUs with a Consensys Base 6U.01 dock.
The IMUs were updated to firmware version LogAndStream v0.11.0, and
managed via the software ConsensysBASIC v1.6.0-64bit on a Dell 7310 laptop with
Microsoft Windows 10. We 3D printed supports (material: PLA) for the sensors to ensure a firm

@@

listed below. The sensors mounted on the cargo bicycle Urban Arrow

@@

sensors for Urban Arrow equipped with the Melia baby shell are shown in

@@

Similarly, the Bugaboo configured to carry 0 months old infants in the baby cot is

@@

  \subcaptionbox{Lateral view}{\includegraphics[width=75mm]{fig/TechDraw_UA-Melia_lat.PNG}}
  \subcaptionbox{Front view}{\includegraphics[width=75mm]{fig/TechDraw_UA-Melia_front.PNG}}

@@

  \subcaptionbox{Lateral view}{\includegraphics[width=75mm]{fig/TechDraw_Bugaboo0_lat.PNG}}

@@

  \item \textbf{Rear Wheel} This IMU was placed on the wheel hub (cargo
  bicycles) or clamped to the wheel (strollers) for measuring the travel speed . The travelling (longitudinal)
  speed was derived according to:

@@

    v = \omega \cdot r

@@

  where \si{\omega} is the angular speed of the wheel (obtained from the IMU's gyroscope aligned with the wheel's axis) and $r$ is the radius of the wheel.
  \item \textbf{Front Wheel} This IMU was mounted on the front wheel fork (the
  caster wheel for the stroller). This was the non-rotating measurement point closest to the
  ground. The purpose of this sensor was to measure the
  road roughness filtered out only by the tyres.  
  \item \textbf{Frame} On the cargo bicycle, an IMU was placed
  below the frontal cargo bay, clamped to the frame. This was to provide an

@@

  with an estimation of the effect of the suspension system. On the
  stroller, the IMU was placed under the baby seat.
  \item \textbf{Seat Head} IMU mounted into the baby seat, directly in
  contact with the dummy's head. This IMU measured the vibration transmitted to the

@@

  \item \textbf{Seat Buttock} This IMU was taped into the baby seat, at the

@@

The IMUs for the seat head and seat buttock 
positions contacting the dummy were placed according to the recommended practice in
vibration testing norms such as ISO-2631-1. This generates acceleration data
representative of the mechanical load transferred from the seat to the human
body taking into account the compliance of the seat foams and the inertia and compliance of the dummy.

The target sampling
frequency was to 910.22~\si{\hertz} for all IMUs. The full-scale range was set to
\(\pm\)16~g for the accelerometer ("WR" or "wide range" configuration on Consensys
Shimmer software), and \(\pm\)2000~\si{\degree\per\second} for the gyroscope. All 
tests were recorded with two GoPro Hero7 cameras: one directly mounted on the
strollers/bicycles to record the dummy-seat relative motion, while the other
was held by an experimenter walking or riding alongside the vehicle to have a
complete overview of the experiment.

\subsubsection{Experimental Protocol}
%
All tests were conducted in Delft, The Netherlands on public
roads near the Delft University of Technology, Faculty of Mechanical
Engineering. Satellite imagery and local photographs of each site are provided in Appendix~\ref{app:location}.
After mounting the sensors and reaching the location
of the experiment, we turned on the sensors to start the experimental session.
Before each trial, we pushed the vehicle back and forth on level ground to mark
the beginning of the trial for time-synchronizing the sensors.
For the cargo bicycle test, a single rider conducted all test runs to be consistent across different sessions (rider mass: 59~\si{\kg};
rider height: 1.70~\si{\m}). We tested on three types of road surfaces with the cargo bicycles and repeated those at different speeds.
The stroller tests were conducted on six different surfaces with the pusher manually
keeping a consistent walking speed of approximately 5~\si{\kilo\meter\per\hour}.  In all tests, speed was controlled by the pusher or cyclist using a speedometer mounted on the stroller handle bar or the steer of the cargo bicycle. 
We gathered data from multiple trials within the same session. The test combinations
are listed below.
%
\begin{itemize}
  \item \textbf{Strollers}  The stroller tests were done with the dummies of 0 months and 9 months old. Some of the test surfaces
  are shown in Figure~\ref{fig:surfaces_stroller} and all are listed below:
  \begin{itemize}
      \item Tarmac
      \item Paver bricks % Klinkers
      \item Sidewalk pavers % Stoeptegels
      \item Cobblestones 
      \item Sidewalk slabs (concrete blocks with gaps in between) % Aula blocks
      \item Shock. A 30x30~\si{\mm} square section aluminium bar was taped to the ground (smooth surface)
  \end{itemize}
  \item \textbf{Cargo bicycles} The cargo bike tests were conducted using
  the dummies of 0 months and 3 months. With the Keiler tricycle, the speed was
  limited to 20~\si{\km\per\hour} for safety reasons (due to wobbling), and
  difficulties to safely keep a constant speed over 22~\si{\km\per\hour}. The test surfaces are listed below:
  \begin{itemize}
      \item Tarmac
      \item Paver bricks
      \item Shock. As mentioned before, we conducted shock test riding over a
      30x30~\si{\mm} square section aluminium bar, at three speeds: 
      \begin{itemize}
          \item Low speed scenario: 5~\si{\km\per\hour}
          \item Medium speed scenario: 12~\si{\km\per\hour}
          \item High speed scenario: 20~\si{\km\per\hour} for the Keiler
          tricycle, 25~\si{\km\per\hour} for the Urban Arrow cargo bicycle.
      \end{itemize}
  \end{itemize}
  \item \textbf{Baby seats} Both were tested on each cargo bicycle using the
  same mounting systems.
  \begin{itemize}
      \item Maxi-Cosi X Joolz Pebble Pro i-Size car seat, it can be adapted to
      cargo bicycles with a proper fixing system ("Urban Arrow Baby Car Seat
      Adapter"). It comes with an integrated suspension system (part of the
      adapter). 
      \item Melia baby shell. The baby seat is meant for babies from 2 to 9
      months, specifically designed for cargo bikes.
  \end{itemize}
\end{itemize}
